Preliminary Thesis Defence

### 2013-12-15 PTD.tex
finish draft uncertainty, move to separate .tex file

\documentclass[a4paper]{report}
\usepackage{color}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage[authordate,backend=biber]{biblatex-chicago}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}

\title{Preliminary Thesis Defense\\~\\
\begin{tabular}{rl}
Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; jean-louis.arcand@graduateinstitute.ch}\\
Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
\end{tabular}
}

@@

\begin{refsection}
\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
\label{unc}
\section*{Abstract}
\textcite{morris1998unique} finds that the introduction of a risk factor leads to a unique equilibrium coming to be in their model of currency attacks.
The self-fullfilling currency attack model which they propose thus has the suprising feature,
that with the introduction of risk perceptions, the multiple equilibria region, thus seems to solve to a single equilibrium.
It is my contention that this is not a surpising result, since the risk factor, replaces a previous existant, Knightian uncertainty, effectively increasing the body of knowledge.
Furthermore, the quantifiable risk only solves a certain part of the multiple equilibria region.
Lastly, if we replace the somewhat stange assumption of a bounded uniform distribution of risk perceptions,
with the more orthodox, normaly distribution, we cannot come to the same results.

\section{The Idea}
\label{unc:idea}
This paper addresses the issue multiple equilibria in models of currency attacks.
In situations of a currency peg, there is the possibility of a currency attack.
Investors will short the pegged currency, hoping the government will release the peg.
If a sufficiently large proportion of the market participates in this,
the cost of maintaining the peg for the government becomes too high,
which will lead to the government releasing the peg.
Currency attacks thus have a self-fulling nature,
which leads to a situation of multiple equilibria,
as described in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}.

In \textcite{morris1998unique} the authors describe such a model
and expand on it by introducting a second-order mechanism.
Hereby investors do not only look at the economics fundamentals of a currency,
but also at other investors' perceptions of these fundamentals.
This leads to a standard situation where there is a stable, unstable, and `ripe for attack' region (based on the economic fundamentals.

However, the authors then proceed to introduce a measure of risk around perceptions by investors.
Investors thus do not know the actual state of the fundamentals, but rather a distored form of it.
As a result, the investors' perception of other investors' perceptions are even more distorted.
Paradoxically, the leads to model being solvable to a unique equilibrium.

\section{The Model}
\label{unc:model}
I will give a brief description of the model as it is defined, and some it features.
There is a state of economic fundamentals $\theta$ which is distributed as $\theta \sim U[0,1]$.
The exchange rate is the hypothetical situation of no government intervention is a function only of these fundamental ($f(\theta)$),
it is assumed that $\frac{\partial f}{\partial \theta} > 0$.
The currency is pegged at a level larger than that derived from the fundamentals ($e* \geq f(\theta)$).
Speculators can short the currency at a cost $t$, their payoff is thus $e* - f(\theta) - t$.

\section{The Results}
\label{unc:results}

\section{The Issues}
\label{unc:issues}
By introduction the idea of perceptions of other investors' perceptions, the authors give a more complete picture of such a currency attack.
It is thus very surprising that the outcome of their more realistic model, correspond less to reality and the more incomplete models.
That is to say, the nature of currency attacks does seem to be characterised by multiple equilibria.
This explicitly expressed by the authors in their introduction, with the mentioning of \textcite{eichengreen1993unstable} and \textcite{dornbusch1994mexico}.

In my understanding of the model, the fact that a unique equilibrium only comes to be with the introduction of a risk factor,
is the result of the fact that this risk factor eliminates the previously existing uncertainty.
In other words, the unique equilibrium is not a surprising result, since Knightian uncertainty is exchanged for quantifiable risk,
which is completer body of knowledge.
This view is enforced by the fact that,
the equilibrium is most pronounced when the risk factor ($\epsilon$) is minimised (i.e.~set equal to zero),
as the authors state themselves.
Furthermore, I have doubts about the authors claim that the domain which is solved by the equilibrium,
is in fact the entire `ripe for attack' domain.

Also, the authors assume that the investors perception of other investors perception takes the form of a bounded uniform distribution.
It is unlikely that perceptions would best be described by a uniform distribution.
More importantly, it is unlikely that this distribution would be bounded, such as is assumed by the authors.
If we replace the bounded uniform distribution, with a normal distribution (which is unbounded),
then we cannot derive the same results.

\nocite{taleb2010black}
\printbibliography
\end{refsection}

>>>>

\documentclass[a4paper]{report}
\usepackage{color}
\usepackage{mathtools}
\usepackage{rotating}
\usepackage{accents}
\usepackage{graphicx}
\usepackage[authordate,noibid,backend=biber]{biblatex-chicago}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}

\title{Preliminary Thesis Defence\\~\\
\begin{tabular}{rl}
Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; jean-louis.arcand@graduateinstitute.ch}\\
Second Reader:&Ugo Panizza\footnote{Professor of Economics, The Graduate Institute, Geneva; ugo.panizza@graduateinstitute.ch}
\end{tabular}
}

@@

\input{uncertainty.tex}
